---
title: "Assignment4"
output: html_document
date: "2025-06-06"
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Divergence or Convergence? Unpacking China’s Provincial Growth Trajectories

Prepared by Caoyu_Shao (Monash-ID:35323876)

Assignment 4 ETC5512

Due date: 2025-06-20

<!-- ---------------------------------------------------------------------- -->

<!-- Data Details -->

<!-- ---------------------------------------------------------------------- -->

## Data Details

#### Topic of this work

Since the reform and opening up, China's economic development has been
changing with each passing day,however, the imbalance of economic
development has always troubled China. This report will study the
relationship between the total economic volume and growth rate of each
province (autonomous region, municipality) since 1993, whether there is
a Matthew effect or an equilibrium situation. Furthermore, we will
explore whether there are different evolution laws in different regions
and different stages.

#### Data Description

The data is a panel data of nearly 34 years from 1990 to 2024, which
includes GDP, GDP per capita, growth rate of GDP per capita, that's because we
think to research the imbalance of development between provinces in China 
mainland and its trends, it's very helpful to conclude the relationship 
between the growth rate of GDP and its volumns.

And GDP has relationship with many variables, many scholars have researched 
about relationship between the growth rate and variables like industrial 
structure, growth rate of fixed asset of investment, urbanization rate, education 
level per capita, degree of opening up to the outside world, scientific and 
technological location.We use the above mentioned variables as control variables in 
this report.

According to Solar Jin(2025), the industrial structure has a significant 
relationship with the growth rate of GDP per capita. He use the ratio of the added 
value of the tertiary industry to the added value of the secondary industry
to measure the deep transformation of industrial structure. He defined it Industrial 
Upgrade Index.In this article, I will use this indicator as an indicator to measure 
our industrial structure

The fixed asset investment growth rate measures the annual percentage change 
in gross fixed capital formation, capturing how much new spending on long-lived 
physical assets. According to Wenyue Li, Jungang Li(2022), the growth rate of fixed 
asset of investment has significantly contributed to the growth of the GDP_per_capita.

The degree of opening up is an indicator referring to how extensively an economy 
engages with the global market through trade, investment, and regulatory integration. 
According to Huiguo Zhang(2017), they concluded that the degree of opening up has 
positive relationship with growth of GDP_per_capita. 

Urbanization rate means that the proportion of the residents who live in urban
areas rather than rural areas. It matters because the residents who live in the
urban areas usually created more GDP in average. 
According to Canjiang Song(2018), they found that the elasticity of urbanization
rate to per capita GDP growth is about 0.15.

The investment on education and the level of R&D funds usually indicate the indensity of human capital. 
More investment in Education , more indensity in human capital and the huamn 
capital is crucial to GDP, commonly speaking, well-educated guys create more GDP.
According to Danjiao Zhan(2021), she found the investment on education has 
contributed to the GDP growth and did a quantitative analysis.According to
Dandan Su, she researched the R&D funds have positive relationship 
with GDP Growth rate.

**Datasets：**


1.  **China's province-by-province permanent population data
    (1993-2023):**
    
    - source: Chinese National Bureau of
      Statistics(<https://data.stats.gov.cn/adv.htm?cn=C01>)
    - content: It includes the population data in every province in
      China mainland from 1993 to 2023
    - recent updated:
    - data form:CSV
    - restrictions: It includes the number of residents in every
      province, but there are still some value not available.For example, the
      number of residents before 2000 are not available.
    - ethics and privacies

   

2.  **China's GDP level by province(1993-2023):**

    - source: Chinese National Bureau of
      Statistics(<https://data.stats.gov.cn/adv.htm?cn=C01>)
    - content: It includes the GDP of 31 provinces in China mainland
      from 1993 to 2023
    - recent updated:
    - data form:
    - restriction: It includes the GDP of all the provinces without
      the population so the GDP per capita is not straight forward.
    - ethics and privacies:
    
    
  

3.  **China's industrial structure by province:**
    
    - source: Chinese National Bureau of
      Statistics(<https://data.stats.gov.cn/adv.htm?cn=C01>)
    - content: It includes the ratio of the added value of the tertiary
      industry to the added value of the secondary industry
      to measure the deep transformation of industrial structure.
    - recent update
    - data form
    - restrictions
    - privacy and ethic risks
    

4.  **Fixed asset investment growth rate by province(2018-2023):**

    - source: Chinese National Bureau of 
      Statistics(<https://data.stats.gov.cn/adv.htm?cn=C01>)
    - content:It includes the data of the growing rate of fixed asset from 2018
      to 2023. 
    - recent update
    - data form:.csv
    - restrictions: There is only the data from 2018 to 2023, so it is not 
      comprehensive. 
    - privacy and ethic risks
    
    
5.  **Urbanization rate by province(2005-2023):**

    - source: Chinese Statistical Yearbook
    - content: It includes the proportion of urban populations from 2005 to 2023
    - recent update
    - data form:.csv
    - restrictions: The time range of the data is from 2005, not comprehensive.
    - privacy and ethic risks

6.  **Human capital level by province:**

    - source: Statistical Bulletin on the Implementation of National Education 
      Funding
    - content:It contains the education investment by regions
    - recent update
    - data form:.xls
    - restrictions: it contains the education investment from 2001.
    - privacy and ethic risks

7.  **Degree of openness by province:**

    - source:Chinese Statistical Yearbook
    - content: It is not very easy to weigh the degree of openness by provinvce.
      Then we come up that we could use the volumn of imports and exports of the
      province. So we use the total volumn of the exports and imports to 
      indicate the degree of openness by province.
    - recent update
    - data form:.xls
    - restrictions:The data is extracted from the Chinese Statistical Yearbook
    - privacy and ethic risks
    


8.**GIS map by province**

         
    -  source:GADM（Global Administrative Areas）(https://gadm.org/download_country_v3.html)，download the china's resource
    -  content
    -  recent updates
    -  data form: .geojson
    -  restrictions:
    -  privacy and ethics risks


9.**Division of economic zones in each province:** 

    - source: Chinese National Bureau of Statistics
(<https://www.stats.gov.cn/zt_18555/zthd/lhfw/2021/rdwt/202302/t20230214_1903926.html>) 
    
    - content: China was divided into four zones according to the Chinese Statistical
      yearbook 
    - recent update
    - data form:csv
    - restrictions: The information is extracted from the html and edited manually.
    - privacy and ethics risks

#### Data download

The following section describes how the data can be downloaded from its
original sources and what initial data wrangling steps have been taken.

```{r}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      eval = FALSE)
                
library(tidyverse)
library(here)
library(sf)
library(patchwork)
library(readr)
library(rvest)
library(stringr)
library(dplyr)
library(tidyr)

```

**Downloading Dataset 1**

```{r}
#pull data 
url = "https://data.stats.gov.cn/english/easyquery.htm?cn=E0103"
# this data is about the number of residents in every province
annual_residents <- read.csv(
  file = "data/Annual_residents.csv",
  header = TRUE,
  stringsAsFactors = FALSE,
  skip = 3
)
annual_residents <- head(annual_residents,-1)
panel_residents <- annual_residents |>
  pivot_longer(
    cols = -Region,
    names_to = "Year",
    values_to = "Residents"
  )
```

**Downloading Dataset 2**

```{r}
#pull data 
url = "https://data.stats.gov.cn/english/easyquery.htm?cn=E0103"
# this data is about the GDP of each province 
annual_gdp <- read.csv(
  file = "data/Annual_gdp.csv",
  header = TRUE,
  stringsAsFactors = FALSE,
  skip = 3
  )

annual_gdp <- head(annual_gdp,-1)


panel_gdp <- annual_gdp |>
  pivot_longer(
    cols = -Region,
    names_to =   "Year",
    values_to = "GDP"
  )


panel_all <- 
  right_join(
    panel_gdp,
    panel_residents,
    by= c("Region","Year")
  )
 
panel_all <- 
   mutate(
     panel_all,
     "GDP_per_capita" = GDP/Residents
     )

panel_all <- panel_all |>
  group_by(Region) |>
  arrange(Year, .by_group = TRUE)|>
  mutate (
    GDP_growth_rate = (GDP - lag(GDP))/lag(GDP),
    GDP_per_capita_growth_rate = (GDP_per_capita - lag(GDP_per_capita))/lag(GDP_per_capita)
  )

 
```

**Downloading Dataset 3**

```{r}

# This  data is the controllable variables


```

**Downloading Dataset 4**

```{r}
The data set is about the growth rate of fixed asset.
# This data is the map and the region separations

```

**Downloading Dataset 10**

```{r}
url =
province_location <-
  read.csv(
    "data/province_location.csv"
    )
panel_all <- 
  panel_all |>
  right_join(
    province_location,
    by = "Region"
    )

```

<!-- ---------------------------------------------------------------------- -->

<!-- Blog post -->

<!-- ---------------------------------------------------------------------- -->

##Blog post

### Why we take the data

### Data source for it

1.数据从哪里得来的 
2.对于数据里面的一些变量做解释 
3.

### what the data tells us?

```{r}
ggplot(
  data =panel_all,
  aes(x= GDP, y= GDP_growth_rate,color =zone))+
  geom_point(size =3, alpha =0.7) +
  geom_smooth(method = "lm",
              se = FALSE,
              linetype = "dashed")+
  labs(
    title = "GDP & Growth Rate by Region",
    x = "gdp(100M )",
    y = "Annual_growth_rate(%)",
    color= "Region"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(hjust =0.5),
    legend.position ="bottom"
  )+
  facet_wrap(~ zone)




```

### So what

### what's really under the surface?

###References

R-packages



Data



Method and inspiration

Jin, S. (2025). Industrial Upgrading and New Quality Productive Forces: Evidence from China's Provincial Panel Data (2003–2022) [Preprint]. arXiv. https://arxiv.org/abs/2501.14258


<!-- ---------------------------------------------------------------------- -->

<!-- Behind the Scenes - Task 3 Tab -->

<!-- ---------------------------------------------------------------------- -->

## Behind the Scene

### What's in the section

#### Question 4

*Tell us about a part(s) of your data processing or analysis that
weren't "sexy" and wouldn't typically be included in a blog post. (e.g.
Was their any data drudgery or time intensive wrangling? Were there any
repetitive tasks or manual tasks? If it was easy, describe what made it
easy?)*

#### Question 5

*Were there any challenges that you faced in conducting this analysis.
These may take the form of data limitations or coding challenges? (e.g.
Was there anything in your analysis that you were not anticipating when
you started? Did you have to change your intended scope?)*

#### Question 6

*Tell us about any imperfect parts of your work or how would like to
expand this analysis in future? (We don't expect you to solve everything
in one assignment.)*

#### Question 7

*An additional 2 marks will be awarded for the code you used to produce
your analysis and report. These marks include reproducibility, compiling
of your .html, production of any figures and tables etc.*
