---
title: "Assignment4"
output: html_document
date: "2025-06-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Divergence or Convergence? Unpacking China’s Provincial Growth Trajectories

Prepared by Caoyu Shao(Monash-ID:35323876)

Assignment 4 ETC5512

Due date: 2025-06-20

<!-- ---------------------------------------------------------------------- -->

<!-- Data Details -->

<!-- ---------------------------------------------------------------------- -->

## Data Details

#### Topic of this work

Since the reform and opening up, China's 
economic development has been changing with 
each passing day,however, the imbalance of 
economic development has always troubled China. 
This report will study the relationship between 
the total economic volume and growth rate of 
each province (autonomous region, municipality)
since 1993, whether there is a Matthew
effect or an equilibrium situation. 
Furthermore, we will explore whether there are 
different evolution laws in different regions
and different stages.

#### Data Description

The data is a panel data of nearly 34 years
from 1990 to 2024, which includes the total GDP
GDP per capita, GDP growth rate, and spatially 
includes 31 provincial-level administrative 
regions in mainland China. The control 
variables include the industrial structure of 
the region, the growth rate of fixed asset 
investment urbanization rate, per capita 
education level, degree of opening up to the 
outside world, scientific and technological 
investment, geographic location.

**Datasets：**

1. **中国逐省份的GDP水平及其增速（1993-2023）：**

    -  来源
    -  内容
    -  最近更新时间
    -  数据类型
    -  限制
    -  隐私和道德风险
    
2. **中国的逐省份人均GDP水平及其增速（1993-2023）：**

    -  来源
    -  内容
    -  最近更新时间
    -  数据类型
    -  限制
    -  隐私和道德风险

3. **中国的逐省份的产业结构、固定资产投资增速、城镇化率、人力资本、对外开放程度、科技投入、地理区位：**
    
    -  来源
    -  内容
    -  最近更新时间
    -  数据类型
    -  限制
    -  隐私和道德风险
    
4.**中国逐省份地理信息图**

    -  来源
    -  内容
    -  最近更新时间
    -  数据类型
    -  限制
    -  隐私和道德风险
    
#### Data download

The following section describes how the data can be downloaded from its original sources and what initial data wrangling steps have been taken.

```{r}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      eval = FALSE)
                
library(tidyverse)
library(here)
library(sf)
library(patchwork)
```

**Downloading Dataset 1**

```{r}
#pull data 
url = "https://data.stats.gov.cn/english/easyquery.htm?cn=E0103"
# this data is about the number of residents in every province

```

**Downloading Dataset 2**
```{r}
#pull data 
url = "https://data.stats.gov.cn/english/easyquery.htm?cn=E0103"
# this data is about the GDP of each province 
```

**Downloading Dataset 3**
```{r}

#this  data is the controllable variables
```

**Downloading Dataset 4**
```{r}

```

<!-- ---------------------------------------------------------------------- -->

<!-- Blog post -->

<!-- ---------------------------------------------------------------------- -->

##Blog post

### Why we take the data 

### Data source for it 
1.数据从哪里得来的
2.对于数据里面的一些变量做解释
3.

### what the data tells us?

### So what

### what's really under the surface?

###References

R-packages

Data

Method and inspiration


<!-- ---------------------------------------------------------------------- -->

<!-- Behind the Scenes - Task 3 Tab -->

<!-- ---------------------------------------------------------------------- -->

## Behind the Scene

### What's in the section

#### Question 4

*Tell us about a part(s) of your data processing or analysis that weren't "sexy" and wouldn't typically be included in a blog post. (e.g. Was their any data drudgery or time intensive wrangling? Were there any repetitive tasks or manual tasks? If it was easy, describe what made it easy?)*

#### Question 5 

*Were there any challenges that you faced in conducting this analysis. These may take the form of data limitations or coding challenges? (e.g. Was there anything in your analysis that you were not anticipating when you started? Did you have to change your intended scope?)*

#### Question 6

*Tell us about any imperfect parts of your work or how would like to expand this analysis in future? (We don't expect you to solve everything in one assignment.)*

#### Question 7

*An additional 2 marks will be awarded for the code you used to produce your analysis and report. These marks include reproducibility, compiling of your .html, production of any figures and tables etc.*